Reply to reviewers concerning submission AAA-D-19-00080R1: "Estimation of the perceived time of presence of sources in urban acoustic environments using deep learning techniques"

### 2019-11-29 paper/submitted/coverLetter2.tex
sub

$\rightarrow$ All elements provided to the reviewers as part of the previous response letter are now presented in the manuscript. In particular, the choice of 45~s long extracts for the listening test and absence of controlled background noise in simulated sound scenes are now included in Section 2.1.

@@

$\rightarrow$ The machine learning corpus is now described in Section 3.1 (instead of Section 2.1). As is now emphasized, its generation procedure is the same as for the simulated sub-corpus of the listening test. However, the isolated samples database is different. Details of the isolated samples database have been added in Section 2.1 and 3.1  for the listening test corpus and the deep learning corpus respectively.

@@

$\rightarrow$ The description of the generation procedure from distributions extracted from the GRAFIC project recordings using simScene has been extended in Section 2.1.

@@

$\rightarrow$ The introduction of Section 4 has been extended to better motivate the objective of this application.

@@

$\rightarrow$ As is now more clearly described in Section 2.1, replicated sound scenes are generated using simScene, with scene composition (scenarios) constrained by annotations of the reference recordings. This differs from the 75 simulated sound scenes for which the scene composition is sampled from gaussian distributions.

@@

$\rightarrow$ As the generation procedure for simulated scenes includes random sampling from distributions, simScene may output similar sound scenes. To avoid this phenomenon in the listening test corpus, 200 scenes are first generated, among which 75 scenes are selected to maximize content diversity.

@@

$\rightarrow$ The selection procedure description has been simplified and Figure 1 has been removed to enhance the reader's comprehension, as the considered indicator for the selection of the 75 simulated scenes was not presented until Section 2.4 (now 3.2).

@@

$\rightarrow$ The sound scenes are scaled so that they are heard at the desired sound level (as measured in the case of recorded and replicated scenes) when using the specific configuration (headphones, sound card) presented in Section 2.2. The term "normalized" has been replaced with "scaled" to avoid confusion.

@@

$\rightarrow$ The term "Likert scale" has been removed throughout the manuscript.

@@

$\rightarrow$ The steps undertaken during the calibration procedure are now detailed in Section 2.2. From this procedure, a simple (linear) relation is obtained between the voltage at the output of the sound card and the sound level produced by the headphones. Sound scenes can be scaled using this information so that they are played at the desired sound level using the specific headphones and sound card configuration.

@@

$\rightarrow$ The 19 replicated scenes are generated by simScene, and thus are not recordings. This part has been rewritten to avoid any confusion in this regard.

@@

$\rightarrow$ All statistical analyses are conducted using Matlab. This is emphasized in the introduction as well as in the beginning of Section 2.5. The code is also made available for further information about the specific functions used.

@@

$\rightarrow$ The description of both equations has been extended to enhance the reader's comprehension.

@@

$\rightarrow$ The Matlab \textit{corrcoef} function was used to compute all correlation coefficients. The corresponding significance test is two-tailed. This is now stated in Section 3.2 and 4.1, where correlation coefficients are presented.

@@

$\rightarrow$ Baseline models of pleasantness are computed on the listening test corpus, as the considered perceptual attributes are available on this corpus only. The baseline model from acoustic indices is computed on a subset of 92 sound scenes as the computation of time of presence estimations requires separated source contributions, which are not available in the 6 recorded scenes. These elements are now more clearly described in Section 4.1.

>>>>

$\rightarrow$ All elements provided to the reviewers as part of the previous response letter are now presented in the manuscript. In particular, the choice of 45~s long extracts for the listening test and absence of controlled background noise in simulated sound scenes are now included in Section 2.1, on rows 255-262 and 204-207 respectively.

@@

$\rightarrow$ The machine learning corpus is now described in Section 3.1 (instead of Section 2.1). As is now emphasized, its generation procedure is the same as for the simulated sub-corpus of the listening test. However, the isolated samples database is different. Details on the contents the isolated samples database have been added in Section 2.1 (rows 197-204) and 3.1 (rows 508-512) for the listening test corpus and the deep learning corpus respectively.

@@

$\rightarrow$ The description of the generation procedure from distributions extracted from the GRAFIC project recordings using simScene has been extended in Section 2.1, with a presentation of simScene simulation modes and inputs on rows 162-193.

@@

$\rightarrow$ The objective of Section 4 is to present a potential application of the proposed detection model to the prediction of higher-level perceptual attributes, and assess the gain of such an approach with respect to known models. The introduction of Section 4 has been extended to better present this motivation.

@@

$\rightarrow$ As is now more clearly described in Section 2.1 (rows 292-299), replicated sound scenes are generated using simScene, with scene composition (scenarios) constrained by annotations of the reference recordings. This differs from the 75 simulated sound scenes for which the scene composition is obtained by sampling from gaussian distributions.

@@

$\rightarrow$ As the generation procedure for simulated scenes includes random sampling from distributions, simScene may output similar sound scenes. To avoid this phenomenon in the listening test corpus, 200 scenes are first generated, among which 75 scenes are selected to maximize content diversity. This is described on rows 262-274 of the revised manuscript.

@@

$\rightarrow$ The dimensions of the mentioned 3D space correspond to the presence (0-100\%) of traffic, voices and birds sources. The 75 simulated scenes of the listening test corpus are selected to be the most isolated, that is distant from others with regard to the euclidean distance, from the original pool of 200 simulated scenes. The selection procedure description has been rewritten on rows 262-274 and Figure 1 has been removed as it did not directly contribute to this description.

@@

$\rightarrow$ The sound scenes are normalized so that they are heard at the desired sound level (as measured in the case of recorded and replicated scenes, or as sampled conditionnally to the ambiance in the case of simulated scenes). This requires the relation between the electrical level at the output of the sound card and the resulting sound level produced by the headphones, which is obtained in Section 2.2.

@@

$\rightarrow$ The term "Likert scale" has been replaced with "semantic differential rating scale" throughout the manuscript.

@@

$\rightarrow$ From the calibration procedure, a simple (linear) relation is obtained between the voltage at the output of the sound card and the sound level produced by the headphones. Sound scenes can be normalized using this information so that they are played at the desired sound level using the specific headphones and sound card configuration. The steps undertaken during the calibration procedure are now detailed in Section 2.2 (rows 315-347).

@@

$\rightarrow$ The 19 replicated scenes are generated by simScene, and thus are not recordings. This part has been rewritten to avoid any confusion in this regard (rows 543-455).

@@

$\rightarrow$ All statistical analyses are conducted using Matlab R2015b with the Statistics and Machine Learning Toolbox v10.1. This is now emphasized in Section 2.5, and reminded where appropriate. The code is also made available for further information about the specific functions used.

@@

$\rightarrow$ Both equations are now presented separately, and each one is more thoroughly explained.

@@

$\rightarrow$ The Matlab \textit{corrcoef} function was used to compute all correlation coefficients. The corresponding significance test is two-tailed. This is now stated in Section 3.2 (rows 632-635) and 4.1 (rows 666-669), where correlation coefficients are presented.

@@

$\rightarrow$ Baseline models of pleasantness are computed on the listening test corpus, as the considered perceptual attributes are available on this corpus only. The baseline model from acoustic indices is computed on a subset of 92 sound scenes as the computation of time of presence estimations requires separated source contributions, which are not available in the 6 recorded scenes. These elements are now more clearly described in Section 4.1 (rows 783-787 and 809-817).
